Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-07-01 paper.qmd
Update readme

Cyclist crashes are underreported in police recorded datasets (Elvik & Mysen, 1999) and the extent of injuries sustained by cyclists may be higher when hospital-recorded cases are counted (Janstrup et al., 2016).
Under-reporting in police datasets is likely to be greatest for minor injuries, while records are seldom kept when a collision or injury is avoided due to riders or drivers taking evasive actions (Ibrahim et al., 2021).
These incidents are often referred to as "near-misses" (Ibrahim et al., 2021).

>>>>

Cyclist crashes are underreported in police recorded datasets [@elvik_incomplete_1999] and the extent of injuries sustained by cyclists may be higher when hospital-recorded cases are counted (Janstrup et al., 2016).
Under-reporting in police datasets is likely to be greatest for minor injuries, while records are seldom kept when a collision or injury is avoided due to riders or drivers taking evasive actions (Ibrahim et al., 2021).
These incidents are often referred to as "near-misses" (Ibrahim et al., 2021).
